---
title: "Week 3 Peer Review"
output: html_document
---

```{r setup, include=FALSE}

######DO NOT MODIFY. This will load required packages and data.

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

cces <- drop_na(read_csv(url("https://www.dropbox.com/s/ahmt12y39unicd2/cces_sample_coursera.csv?raw=1")))

cel <- drop_na(read_csv(url("https://www.dropbox.com/s/4ebgnkdhhxo5rac/cel_volden_wiseman%20_coursera.csv?raw=1")))

```

Following the directions on the Coursera assignment page, you will make four original visualizations. Note that the data for the CCES and CEL data are imported in code in the R Markdown file.

### Put your name here: Mehwish Younus

## Exercise 1

Explain what you are visualizing here:

Here, I am visualing the number of total members in 115th congress distributed by their gender and stacked by power in the congress.

Put your figure here:

```{r exercise1,echo=FALSE}

####PUT YOUR CODE HERE
congress<-cel%>%filter(congress==115)
congress$female<-recode(congress$female, '0'="male", '1'="female")
congress$power<-recode(congress$power, '0'="No power", '1'="Has power")
congress%>%ggplot(aes(x=female, fill=power))+geom_bar()+theme_classic()+labs(xlab="Gender", ylab="No.of males & females", title = "Members in 115th congress with their status")

```

## Exercise 2

Explain what you are visualizing here:

I am visualizing the seniority status of member using a box plot. Whether a male has more experience or a female. There are a few outliers in male indicating that some males have more seniority than females.

Put your figure here:

```{r exercise2,echo=FALSE}

####PUT YOUR CODE HERE
# Subset the data for 'male' and 'female' separately
male_subset <- congress[congress$female == 'male', ]
female_subset <- congress[congress$female == 'female', ]
summary(male_subset$seniority)
summary(female_subset$seniority)
congress%>%ggplot(aes(x=female,y=seniority))+geom_boxplot()+labs(xlab="Gender", ylab="Seniority in Congress", title="Member Seniority in 115th congress")+theme_bw()+annotate("text", x=2, xend=2.5, y=30, yend=35, label="Outliers")+annotate("rect", xmin=0.9, xmax=2.2, ymin=17, ymax=28, alpha=0.5)
```

## Exercise 3

Explain what you are visualizing here:

I am trying to visualize how many bills were passed as member efficiency distributed by males and females. Republican party was able to pass more bills in both genders.

Put your figure here:

```{r exercise3,echo=FALSE}

####PUT YOUR CODE HERE
congress$dem<-recode(congress$dem, '0'="Republican", '1'="Democrat")
congress<-congress%>%rename(party = dem)
congress%>%ggplot(aes(x=all_bills, y=all_pass, color=party))+geom_point()+facet_wrap(.~female)+scale_color_manual(values=c("blue", "red"))+labs(x="Bills Presented", y="Bills Passed", title="Member Efficiency to pass bills")+theme_classic()
```

## Exercise 4

Explain what you are visualizing here:

I am trying to explain how the member ideology changes over time by distributing them into genders.


Put your figure here:

```{r exercise4,echo=FALSE}

####PUT YOUR CODE HERE

congress%>%ggplot(aes(x=elected, y=dwnom1))+geom_line()+facet_wrap(.~female)+theme_bw()+labs(x="Year elected", y="DW-Nominate score",title="Member ideology score distributed by gender over years")


```
