---
title: "Week 2 Peer Review"
output: html_document
---

```{r setup, include=FALSE}

######DO NOT MODIFY. This will load required packages and data.

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
cces <- drop_na(read_csv(url("https://www.dropbox.com/s/ahmt12y39unicd2/cces_sample_coursera.csv?raw=1")))
```

Your objective is to replicate these figures, created using the Cooperative Congressional Election Study data. These figures are similar to those we completed in the lecture videos.

### Put your name here: Mehwish



## Exercise 1

Hints:

* For the x-axis, use the variable "ideo5".

* Make sure you recode the data for the "ideo5" variable to generate the correct names for the x-axis. You will want to consult the codebook.

* Use the fill aesthetic to have R fill in the bars. You do not need to set the colors manually.

* Use guides() to drop the legend.

* Make sure the axis labels and figure title are correct.


```{r exercise1,echo=FALSE}
####PUT YOUR CODE HERE
cces$ideo5<-recode(cces$ideo5, '1'="Very liberal", '2'="Liberal", '3'="Moderate", '4'="Conservative", '5'="Very Conservative")
cces%>%ggplot(aes(x=ideo5,fill=ideo5))+geom_bar()+labs(x="Ideology",title="Respondant Ideology")

```

## Exercise 2

Hints:

* For the x-axis, use the variable "pew_religimp".

* Make sure you recode the data for the "pew_religimp" variable to generate the correct labels for the x-axis. You will want to consult the codebook.

* Rename the column for Ideology to make sure the first letter is upper-case (to make the legend appear correctly).

* Use the fill aesthetic to have R fill in the bars. You do not need to set the colors manually.

* Make sure the axis labels and figure title are correct.

```{r exercise2,echo=FALSE}
####PUT YOUR CODE HERE
cces$pew_religimp<-recode(cces$pew_religimp, '1'="Very Important", '2'="Somewhat Important", '3'="Not too important", '4'="Not at all important")
cces<-cces%>%rename(Ideology=ideo5)
cces%>%ggplot(aes(x=pew_religimp,fill=Ideology))+geom_bar()+labs(x="Ideology", title="Ideology and Religion")+theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Exercise 3

Instructions:

* For this visualization, you are creating your own data for practice.

* Create a tibble/data frame with three columns: Semester, Student, and Grade.

* There should be six semesters and three students (Amanda, Betty, and Carol)

* Create grades for the students using the runif() command, with values between 80 and 100. Hint: you'll need 18 grades total.

The figure should look approximately like this (your vaules will be slightly different):


```{r exercise3,echo=FALSE}
####PUT YOUR CODE HERE
Grades=runif(18,min=80,max=100)
Students=c("Amanda","Betty","Carol")
Semesters <- rep(1:6, each = length(Students))
data<-data.frame(Students, Semesters, Grades)
data%>%ggplot(aes(x=Semesters, y=Grades, color=Students))+geom_line()+facet_wrap(.~Students)

```
